\documentclass[11pt,letterpaper]{article}
\usepackage{array, xcolor, lipsum, bibentry}
\usepackage[left=0.6in, right=0.6in, top=0.7in, bottom=0.7in]{geometry} % margins
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{etaremune}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{natbib}


%\usepackage{bibentry}
%\usepackage{sectsty}
%\sectionfont{\fontsize{10}{12}\selectfont}

%\setlist{nosep} % or \setlist{noitemsep} to leave space around whole list
\setlist{noitemsep}
\setlength\parindent{0pt}

\begin{document}
\pagestyle{headings}
\markright{\textbf{Resume} Prepared \today}
%\section*{Lijie Ding}
\begin{center}
    \huge{\textbf{Lijie Ding}} \\
\end{center}
\vspace*{-0.in}
%\textbf{Current position}: Associate at Goldman Sachs \\
\textbf{Contact}: (401)-410-4049, ljding.jobs@gmail.com
~~\textbf{Link}: \href{https://github.com/ljding94}{Github}, \href{https://www.linkedin.com/in/lijie-ding-305b04171/}{LinkedIn}, \href{https://scholar.google.com/citations?user=i-U0wBsAAAAJ&hl=en&oi=ao}{Google Scholar}
%\href{https://ljding94.github.io}{Homepage}

\begin{comment}
\begin{center}
    \begin{tabular}{l l l}
        Associate at Goldman Sachs & (401)-410-4049 & ljding.jobs@gmail.com \\
        \href{https://github.com/ljding94}{Github} & \href{https://www.linkedin.com/in/lijie-ding-305b04171/}{LinkedIn} & \href{https://scholar.google.com/citations?user=i-U0wBsAAAAJ&hl=en&oi=ao}{Google Scholar}
        %\href{https://ljding94.github.io}{Homepage}
    \end{tabular}
\end{center}
\end{comment}

\vspace*{-0.1in}
\section*{Education}
\vspace*{-0.1in}
Ph.D. (Physics), Brown University \hfill  10/2022  %10/16/2022
\newline
Dissertation: Chiral Liquid Crystals on Deformable Surfaces: A Monte Carlo Study
\newline
Advisor: Robert A. Pelcovits and Thomas R. Powers
\vspace*{-0.1in}
\\~\\
B.Sc. (Applied Physics), University of Science and Technology of China (USTC) \hfill 06/2017%06/19/2017
\newline
Thesis: Irreversible Monte Carlo Algorithms
\newline
Advisor: Youjin Deng

\vspace*{-0.1in}
\section*{Experience}
\vspace*{-0.05in}



%\textbf{Price Verification (PV) for Interest Rate (IR) Derivatives, \emph{Goldman Sachs}}  \hfill 07/2022 - present~
%\vspace*{-0.05in}
%\begin{itemize}
%    \item Calibrated pricing models' inputs to mark to market valuation using market data/consensus sourced.
%    \item Conducted first order PV attribution analysis respect to risk factors: IR Basis/Xccy, FX spot.
%    \item Performed product-level PV analysis of \emph{exotic derivatives}: Bermudan Swaption, CMSBinary etc.
%    \item Developed SOFR PV models, expanded data scope, tested financial impact using \emph{statistical data analysis}.

\textbf{Development and Maintenance of Valuation Models, \emph{Goldman Sachs}}  \hfill 07/2022 - present~
\vspace*{-0.05in}
\begin{itemize}
    \item Calibrated pricing models' inputs to mark to market valuation using market data and consensus.
    \item Covered product-level valuation models of \emph{exotic derivatives}: Bermudan Swaption, CMSBinary etc.
    \item Developed calibration and valuation models based on SOFR, and expanded scope of sourced data.
\end{itemize}

\textbf{Data Analysis for Market Consensus and Inventory Securities, \emph{Goldman Sachs}}  \hfill 07/2022 - present~
\vspace*{-0.05in}
\begin{itemize}
    \item Conducted first-order attribution analysis respect to risk factors: IR Basis/Xccy, FX spot.
    \item Developed analysis tools for tracking risk and valuation of Bermudan Swaption and Cancellable Swap.
    \item Expanded attribution analysis tool for inventory securities' price variance from market implied valuation.
\end{itemize}

\textbf{Monte Carlo Simulation of Chiral Fluid Membrane, \emph{Brown University}} \hfill 05/2018 - 08/2023
\vspace*{-0.05in}
\begin{itemize}
    \item Developed \emph{quantitative modeling} frameworks for colloidal membrane using \emph{Monte Carlo method}.
    \item Executed off-lattice dynamical triangulation simulation developed in \emph{C++} on \emph{high performance computing cluster} managed by \emph{Slurm} using \emph{Bash Script}.
    \item Developed \emph{statistical analysis}, \emph{uncertainty analysis} method and \emph{data visualization} using \emph{Python}.
\end{itemize}

\textbf{Controlled Amplification of DNA Brownian Motion, \emph{Brown University}} \hfill 10/2017 - 11/2020
\vspace*{-0.05in}
\begin{itemize}
    \item Solved overdamped \emph{Brownian Motion}, Langevin dynamics, for $\lambda$DNA under electric stochastic noise.
    \item Developed \emph{image analysis} and tracking software using \emph{Python} for fluorescent $\lambda$DNA in nanoslit.
    \item Developed \emph{time series analysis} and error analysis, \emph{bootstrapping}, for $\lambda$DNA \emph{Brownian motion} trajectory.
\end{itemize}

\textbf{Irreversible Monte Carlo (MC) Algorithms, \emph{USTC}} \hfill 06/2015 - 11/2017
\vspace*{-0.05in}
\begin{itemize}
    \item Investigated and designed irreversible \emph{MC algorithms}: Event-Chain Parallel Tempering and Lifted Worm, achieved up to \emph{25\%} and \emph{14,000\%} efficiency improvement, respectively.
    \item Developed and implemented these algorithms using \emph{object-oriented programming} with \emph{C++}.
    \item Analyzed and benchmarked MC sampling data using advanced \emph{data analysis}, \emph{Sokal's auto-windowing method}, carried out \emph{data visualization} for publication using \emph{Python}.
\end{itemize}

\vspace*{-0.1in}
\section*{Skills/Knowledge}
\vspace*{-0.1in}
\textbf{Software/Programming}: Excel, C++, Python, Bash, Mathematica, Matlab. \newline
\textbf{Technical}: Monte Carlo Method, Time Series Analysis, Statistical Data Analysis, Algorithm Development\newline
\textbf{Finance}: Interest Rate Derivatives, Stochastic Calculus, Mathematical/Quantitative Finance

\vspace*{-0.1in}
\section*{Publications}
\vspace*{-0.1in}
\textbf{Monte Carlo}: \href{https://doi.org/10.1039/D3SM01158E}{Ding2023SoftMatter}, \href{https://doi.org/10.1039/D1SM00629K}{Ding2021SoftMatter}, \href{https://doi.org/10.1103/PhysRevE.102.032608}{Ding2020PRE}, \href{https://doi.org/10.1103/PhysRevE.97.042126}{El{\c{c}}i2018PRE} \newline
\textbf{Brownian Motion}: \href{https://doi.org/10.1103/PhysRevApplied.14.054042}{Lameh2020PRApplied} \newline
\textbf{Others}: \href{https://doi.org/10.1088/2058-8585/ab10f5}{Khan2019Flex.PE}, \href{https://doi.org/10.48550/arXiv.1610.02768}{Wei2016Arxiv}

\begin{comment}
\vspace*{-0.1in}
\section*{Awards}
\vspace*{-0.1in}
\textbf{Physics}: Dissertation Fellowship(Brown 2021), Grand Price(CUPT 2015), Bronze Medal(CPhO 2012) \newline
\textbf{General}: National Scholarship (China 2015 and 2016)
\end{comment}


\end{document}