\documentclass[11pt,letterpaper]{article}
\usepackage{array, xcolor, lipsum, bibentry}
\usepackage[left=0.65in, right=0.65in, top=0.85in, bottom=0.85in]{geometry} % margins
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{etaremune}
\usepackage[numbers]{natbib}
\usepackage{hyperref}

%\setlist{nosep} % or
\setlist{noitemsep}%  to leave space around whole list
\setlength\parindent{0pt}

\begin{document}
\pagestyle{headings}
%\markright{VITA Prepared \today}
%\footnote{VITA Prepared \today}
\begin{center}
    \Large{\textbf{CURRICULUM VITAE}}
\end{center}
\section*{Lijie Ding}
\vspace*{-0.15in}
\begin{longtable}{p{0.5\linewidth} p{0.5\linewidth}}
    Neutron Scattering Division, \newline
    Oak Ridge National Laboratory \newline
    Oak Ridge, TN, 37830, U.S.
     & ~\newline
    % xxx-xxx-xxxx \newline
    %Lijie\_Ding@Brown.edu
    %lijie\_ding@alumni.brown.edu
    dingl1@ornl.gov
\end{longtable}


\section*{Appointments}
\vspace*{-0.15in}
\begin{longtable}{l p{\linewidth}}
    May 2024 - present  & Postdoctoral Research Associate, Oak Ridge National Laboratory \\
    Jan 2024 - May 2024 & Vice President, Quantitative Strategist, Goldman Sachs \\
    Jun 2022 - Dec 2023 & Associate, Quantitative Strategist, Goldman Sachs \\
\end{longtable}


\section*{Education}
\vspace*{-0.15in}
\begin{longtable}{l p{\linewidth}}
    Sep 2017 - Jun 2022   & Ph.D. in Physics, Brown University \newline
    Dissertation: Chiral Liquid Crystal on Deformable Surfaces: A Monte Carlo Study \newline
    Advisor: Robert A. Pelcovits and Thomas R. Powers                                                 \\~\\
    Sep 2013 - Jun 2017   & B.Sc. in Applied Physics, University of Science and Technology of China \newline
    Thesis: Irreversible Monte Carlo Algorithms \newline
    Advisor: Youjin Deng
\end{longtable}

\section*{Skills}
\vspace*{-0.15in}
\begin{longtable}{l p{0.76\linewidth}}
    Scientific Computing & Monte Carlo, Molecular Dynamics, LAMMPS, HOOMD-blue, HPC, Slurm\\~\\
    Programming & Python, C/C++, PyTorch, CrewAI, LangChain, NumPy, SciPy, Pandas, Scikit-learn, SQL, Bash \\~\\
    Domain Knowledge & Agentic AI, Computational Physics, Soft Matter Physics, Small-Angle Scattering, Statistical Physics, Polymer Physics, Deep Learning, Machine Learning, Quantitative Finance
\end{longtable}

\section*{Publications}
%\bibliographystyle{plain}
%\bibliographystyle{unsrt}
\bibliographystyle{plainnat}
\nobibliography{publication}

\subsection*{Journal Articles}
\begin{etaremune}
    \item \bibentry{ding2026topolyagent}
    \item \bibentry{tung2025BayesianNSE}
    \item \bibentry{tung2025Bayesian}
    \item \bibentry{ding2025pdHS}
    \item \bibentry{tung2025universalGPR}
    \item \bibentry{ding2024MLsemiflexiblepolymer}
    \item \bibentry{ding2025chargedpolymer}
    \item \bibentry{ding2025ladderpolymer}
    \item \bibentry{ding2025shearedcolloids}
    \item \bibentry{ding2025decipheringpolymer}
    \item \bibentry{tung2025unlocking}
    \item \bibentry{tung2025insights}
    \item \bibentry{huang2025elongated}
    \item \bibentry{tung2025scattering}
    \item \bibentry{Tung2024Adiscretized}
    \item \bibentry{ding2024offlattice}
    \item \bibentry{ding2023chiral}
    \item \bibentry{ding2021deformation}
    \item \bibentry{ding2020shapes}
    \item \bibentry{lameh2020controlled}
    \item \bibentry{khan2019yourself}
    \item \bibentry{elcci2018lifted}
\end{etaremune}

\subsection*{Preprints}
\begin{etaremune}
    \item \bibentry{ding2025llms}
    \item \bibentry{du2025protocolrouter}
    \item \bibentry{ding2025dlpricing}
    \item \bibentry{ding2025sasagent}
    \item \bibentry{ding2025fastGPRpricing}
    \item \bibentry{ding2025brownian}
\end{etaremune}

\subsection*{In preparation}
\begin{etaremune}
    \item \bibentry{ding2025rods}
\end{etaremune}

\section*{Presentations}
\subsection*{Invited Talks}
\begin{etaremune}
    \item LLMs Can Assist with Proposal Selection at Large User Facilities. Neutron Day 2026, Oak Ridge National Laboratory (Jan. 2026)
    \item Machine Learning for Scattering Analysis and Derivative Valuation. Condensed Matter and Biophysics Seminar. Brown University (Sep. 2025)
    \item Machine Learning for Derivative Valuation with Volatility Surfaces. Large Scale Structures Seminar Series, Neutron Scattering Division, Oak Ridge National Laboratory. (Sep. 2025)
    \item Examples of Machine Learning for Small-Angle Scattering. Joint Nanoscience and Neutron Scattering User Meeting. Knoxville. (Aug. 2025)
    \item Mechanically Driven Polymers: Monte Carlo Simulation and Machine Learning-Assisted Scattering Analysis. SMART forum. Oak Ridge National Laboratory (Apr. 2025)
    \item Machine Learning-Assisted Inference of Sheared Suspension using Scattering. Neutron Scattering Day, Oak Ridge National Laboratory. (Jan. 2025)
    \item Characterizing structure of ladder polymer using machine learning assisted scattering data analysis. AI for Neutrons Workshop, Oak Ridge National Laboratory (Oct. 2024)
    \item Shapes and orientational order of colloidal membrane. Oak Ridge National Laboratories (Apr. 2022), Johns Hopkins University (Apr. 2022), Instituto Gulbenkian de Ciência (Apr. 2022), Merck (Mar. 2022), Rice University (Feb. 2022), Sandia National Laboratories (Dec. 2021)
\end{etaremune}

\subsection*{Contributed Talks}
\begin{etaremune}
    \item Extracting properties of charged polymers from scattering using Machine Learning. AI4Science Workshop, ORNL (Apr. 2025)
    \item Characterizing structure of ladder polymer using machine learning assisted scattering data analysis. ACS Spring meeting, session on General Topics: New Synthesis and Characterization of Polymers. San Diego (Mar. 2025)
    \item Monte Carlo Simulation and Machine Learning-Assisted Scattering Analysis of Mechanically Driven Polymers. APS Global Physics Summit, session on Machine Learning and Optimization for Accelerating Polymer Physics. Anaheim (Mar. 2025)
    \item Characterizing structure of ladder polymer using machine learning assisted scattering data analysis. 99th New England Complex Fluids Meeting Brown University (Jun. 2024)
    \item Three-dimensional structures of chiral membrane with edges, APS March Meeting, Session on Membranes, Micelles and Vesicles. Chicago (Mar. 2022)
    \item 3D structures of chiral membrane with edges. 89th New England Complex Fluids Meeting. Harvard University (Dec. 2021)
    \item Chiral membranes with orientational order and free edges, APS March Meeting, Session on Membranes, Micelles and Vesicles. Online (Mar. 2021)
    \item Membranes with orientational order and free edges. 86th New England Complex Fluids Meeting. Online (Mar. 2021)
    \item Shapes of fluid membrane with chiral edges. 81st New England Complex Fluids Meeting. Harvard University (Dec. 2019)
\end{etaremune}

\subsection*{Posters}
\begin{etaremune}
    \item Mechanically Driven Polymers: Monte Carlo Simulation and Machine Learning Scattering Analysis (and more). Southeast Polymer Forum, University of Georgia  (May. 2025)
    \item Characterizing structure of ladder polymer using machine learning assisted scattering data analysis. Southeast Polymer Forum, Oak Ridge National Laboratory (Oct. 2024)
    \item 3D structures of chiral membranes with free edges. Mechanics of Life workshop, Flatiron Institute (May. 2022)
    \item 3D structures of chiral membranes with free edges. Physics Department Poster Session. Brown University(Nov. 2021)
    \item Membranes with orientational order and free edges. Physics Department Poster Session. Brown University(Nov. 2020)
    \item Shapes of fluid membrane with chiral edges. Physics Department Poster Session. Brown University (Nov. 2019)
    \item Membranes with edges. Materials Research Science and Engineering Centers Retreat. Brandeis University (Nov. 2018)
\end{etaremune}

%\section*{Support}
%\vspace*{-0.15in}
%\begin{longtable}{l p{\linewidth}}
%    May. 2025 - Aug. 2025 & ORNL Research Student Internship Mentoring Program. \newline (mentor with co-mentor: Changwoo Do) \$13,838
%\end{longtable}

\section*{Mentoring}
\vspace*{-0.15in}
\begin{longtable}{l p{\linewidth}}
    Simon Nirenberg (Brown 2028) & Research student internship program, (Summer 2025)
\end{longtable}

\section*{Teaching}
\vspace*{-0.15in}
\begin{longtable}{l p{\linewidth}}
    %Sep 2017 - Jun 2018    & Teaching Assistant (Basic Physics A, B), Brown University \\
    %Sep 2016 - Dec 2016    & Teaching Assistant (Mechanics and Thermal Physics), USTC
    Teaching Assistant & Basic Physics B, Brown University (Spring 2018) \\
    Teaching Assistant & Basic Physics A, Brown University (Fall 2017) \\
    Teaching Assistant & Mechanics and Thermal Physics, USTC (Fall 2016)
\end{longtable}


\section*{Professional Activities}
\vspace*{-0.15in}
\begin{itemize}
    \item Reviewer, Computational Economy (Dec 2025)
    \item Reviewer, Machine Learning with Application (Aug. 2025)
    \item Presider, ACS Spring Meeting, Session on General Topics: New Synthesis and Characterization of Polymers. San Diego (Mar. 2025)
    \item Reviewer, Scientific Reports. (Jun. 2024)
\end{itemize}

\section*{Awards and Honors}
\vspace*{-0.15in}
\begin{longtable}{l p{\linewidth}}
    2025 & Faculty Poster Award, Southeast Polymer Forum, University of Georgia, U.S. \\
    2021 & Physics Dissertation Fellowship, Brown University, U.S.    \\
    2016 & National Scholarship, Ministry of Education, China         \\
    2015 & Grand Prize, China Undergraduate Physics Tournament, China \\
    2015 & National Scholarship, Ministry of Education, China         \\
    2012 & Bronze Medal, Chinese Physics Olympiad, China              \\
\end{longtable}

\section*{}
VITA Prepared \today
\end{document}
