\documentclass[11pt,letterpaper]{article}
\usepackage{array, xcolor, lipsum, bibentry}
\usepackage[left=0.6in, right=0.6in, top=0.5in, bottom=0.5in]{geometry} % margins
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{etaremune}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{natbib}


\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

%\usepackage{bibentry}
%\usepackage{sectsty}
%\sectionfont{\fontsize{10}{12}\selectfont}

%\setlist{nosep} % or \setlist{noitemsep} to leave space around whole list
\setlist{noitemsep}
\setlength\parindent{0pt}

\begin{document}
%\pagestyle{headings}
\pagestyle{empty}
%\markright{\textbf{Resume} Prepared \today}
%\section*{Lijie Ding}
\begin{center}
    \huge{\textbf{Lijie Ding}} \\
\end{center}
\vspace*{-0.in}
%\textbf{Current position}: Associate at Goldman Sachs \\
\textbf{Contact}: (401)-410-4049, ljding.jobs@gmail.com
~~\textbf{Link}: \href{https://github.com/ljding94}{Github}, \href{https://www.linkedin.com/in/lijie-ding-305b04171/}{LinkedIn}, \href{https://scholar.google.com/citations?user=i-U0wBsAAAAJ&hl=en&oi=ao}{Google Scholar}
%\href{https://ljding94.github.io}{Homepage}

\begin{comment}
\begin{center}
    \begin{tabular}{l l l}
        Associate at Goldman Sachs & (401)-410-4049 & ljding.jobs@gmail.com \\
        \href{https://github.com/ljding94}{Github} & \href{https://www.linkedin.com/in/lijie-ding-305b04171/}{LinkedIn} & \href{https://scholar.google.com/citations?user=i-U0wBsAAAAJ&hl=en&oi=ao}{Google Scholar}
        %\href{https://ljding94.github.io}{Homepage}
    \end{tabular}
\end{center}
\end{comment}

\begin{comment}
\vspace*{-0.1in}
\section*{Education}
\vspace*{-0.1in}
Ph.D. (Physics), Brown University \hfill  10/2022  %10/16/2022
\newline
Dissertation: Chiral Liquid Crystals on Deformable Surfaces: A Monte Carlo Study
\newline
Advisor: Robert A. Pelcovits and Thomas R. Powers
\vspace*{-0.1in}
\\~\\
B.Sc. (Applied Physics), University of Science and Technology of China (USTC) \hfill 06/2017%06/19/2017
\newline
Thesis: Irreversible Monte Carlo Algorithms
\newline
Advisor: Youjin Deng
\end{comment}

% EXPERIENCE
\vspace*{-0.1in}
\section*{Experience}
\vspace*{-0.05in}
\textbf{Oak Ridge National Laboratory (ORNL)} \hfill Oak Ridge, TN \\
\textit{Postdoctoral Research Associate (Neutron Scattering Division)} \hfill May 2024 -- Present
\begin{itemize}[leftmargin=*]
    \item \textbf{Multi-Agent Systems:} Developed "SasAgent," a multi-agent AI system used to automate complex small-angle scattering data analysis, integrating domain-specific tools with LLM orchestration.
    \item \textbf{LLM Application Development:} Engineered "ToPolyAgent" and protocol routing frameworks to assist with coarse-grained topological simulations and user facility proposal selection.
    \item \textbf{Deep Learning for Inverse Problems:} Designed and trained deep learning models to decipher structural properties of polymers and colloids from scattering data, significantly accelerating analysis speed compared to traditional fitting.
    \item \textbf{Scientific Machine Learning:} Collaborated on Bayesian inference and Gaussian Process Regression (GPR) models to unlock hidden information in sparse measurement data.
\end{itemize}
\vspace{0.05in}

\textbf{Goldman Sachs} \hfill New York, NY \\
\textit{Vice President, Quantitative Strategist} \hfill Jan 2024 -- May 2024 \\
\textit{Associate, Quantitative Strategist} \hfill Jun 2022 -- Dec 2023
\begin{itemize}[leftmargin=*]
    \item \textbf{Financial Modeling:} Developed and calibrated valuation models for exotic derivatives (Bermudan Swaptions, CMS Binary) and inventory securities.
    \item \textbf{Data Analysis Pipeline:} Built large-scale attribution analysis tools to track price variance against market consensus and risk factors (IR Basis/Xccy, FX spot).
    \item \textbf{ML Research:} Conducted research on applying Deep Learning and Machine Learning to option pricing and volatility surfaces, bridging traditional quantitative finance with modern AI techniques.
    \item \textbf{Statistical Analysis:} Expanded data scope and performed rigorous statistical testing for SOFR-based pricing models.
\end{itemize}
\vspace{0.05in}

\textbf{Brown University} \hfill Providence, RI \\
\textit{Ph.D. Researcher (Computational Physics)} \hfill Sep 2017 -- Jun 2022
\begin{itemize}[leftmargin=*]
    \item Developed high-performance C++ simulation frameworks for Monte Carlo studies of soft matter systems.
    \item Implemented parallel algorithms on HPC clusters (Slurm) and developed Python pipelines for statistical data analysis and visualization.
\end{itemize}

% SKILLS
\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Machine Learning \& AI:} Large Language Models (LLMs), Multi-Agent Systems, Deep Learning (CNNs, MLPs), Gaussian Processes, Bayesian Inference, Generative AI.
    \item \textbf{Programming \& Data:} Python (PyTorch, NumPy, SciPy, Pandas, Scikit-learn), C++, SQL, Bash.
    \item \textbf{Tools \& Platforms:} Git, Linux, High-Performance Computing (Slurm), LaTeX.
    \item \textbf{Domain Knowledge:} Quantitative Finance (Derivatives Pricing), Computational Physics (Monte Carlo), Time Series Analysis.
\end{itemize}

\begin{comment}
% SELECTED PUBLICATIONS
\section*{Selected AI \& ML Publications (2025)}
\begin{itemize}[leftmargin=*]
    \item \textbf{L. Ding}, et al. "SasAgent: Multi-Agent AI System for Small-Angle Scattering Data Analysis." \textit{arXiv:2509.05363} (2025).
    \item \textbf{L. Ding}, et al. "LLMs Can Assist with Proposal Selection at Large User Facilities." \textit{arXiv:2512.10895} (2025).
    \item \textbf{L. Ding}, et al. "Deep Learning Option Pricing with Market Implied Volatility Surfaces." \textit{arXiv:2509.05911} (2025).
    \item \textbf{L. Ding}, et al. "ToPolyAgent: AI Agents for Coarse-Grained Topological Polymer Simulations." \textit{arXiv:2510.12091} (2025).
    \item \textbf{L. Ding}, C. Do. "Deciphering the small-angle scattering of polydisperse hard spheres using deep learning." \textit{APL Machine Learning} (2025).
\end{itemize}
\end{comment}
% EDUCATION
\section*{Education}
\textbf{Brown University} \hfill Providence, RI \\
Ph.D. in Physics (Dissertation: Chiral Liquid Crystals on Deformable Surfaces) \hfill 2022 \\
\textbf{University of Science and Technology of China (USTC)} \hfill Hefei, China \\
B.Sc. in Applied Physics \hfill 2017

\begin{comment}
\vspace*{-0.1in}
\section*{Awards}
\vspace*{-0.1in}
\textbf{Physics}: Dissertation Fellowship(Brown 2021), Grand Price(CUPT 2015), Bronze Medal(CPhO 2012) \newline
\textbf{General}: National Scholarship (China 2015 and 2016)
\end{comment}


\end{document}